---
title: "HW 6"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


Load key packages

```{r}
library(p8105.datasets)
library(modelr)
library(purrr)
```

## Problem 2

Creating a `city_state` variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omitting cities Dallas, TX; Phoenix, AZ; and Kansas City, MO as these don’t report victim race. Also omiting Tulsa, AL as this is a data entry mistake. For this problem, limit the analysis those for whom victim_race is white or black. Ensuring that victim_age is numeric.

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) |> 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age)
  )
```

